---
title: "Analyze Twitter Network"
author: "GuyGo and Ofri Masad"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(igraph)
setwd("C:/Users/Guy Gonen/PycharmProjects/TweeterNetwork/")
ga.data <- read.csv('edges_no_duplicates.csv', header = T)
g <- graph.data.frame(ga.data,directed = F)
g <- simplify(g)
```


# Network Analysis:
### Reading the data
The data is a csv files containing the graph edges of GuyGo twitter followers.
And edge is represented by couple: {From, To}
```{r read_data, cache=TRUE}
head(ga.data)
```
### Data exploration:
#### Followers:
We've fetched information from CatcherGG[Guy Gonen] and his 134 followers.
For each follower we fetched up to 200 possible followers and then dropped people which are not following CatcherGG In order to not exceed 200 nodes.
```{r relations, cache=TRUE}
V(g)$name
```
#### Number of Connections between followers and followers of followers:
```{r number_of_relations, cache=TRUE}
summary(g)
```

### Data-visualization:
#### Basic representation:
```{r basic, cache=TRUE}
g$layout <- layout.fruchterman.reingold(g)
plot(g)
```  
#### Basic representation without names [We'll continue without names from now on]:
```{r basic_rep2, cache=TRUE}
V(g)$label <- NA 
g$layout <- layout.fruchterman.reingold(g)
plot(g)
```
#### Degree score:
```{r degree, cache=TRUE}
degr.score <- degree(g)
degr.score
V(g)$size <- degree(g) * 0.3 
plot(g)
```

#### Closeness centrality:
```{r closeness_cent, cache=TRUE}
clo <- closeness(g) 
V(g)$color <- "gray"
V(g)$size <- clo * 1000
V(g)$label <- NA
plot(g)
clo
which.max(clo)
```  

As expected, CatcherGG is the most central.


#### Betweeness centrality.
```{r betweeness_cent, cache=TRUE}
btw <- betweenness(g) 
V(g)$color <- "gray"
V(g)$size <- btw/400
V(g)$label <- NA
plot(g)
btw
which.max(btw)
```  

As expected, CatcherGG is the most central.

#### Eigenvector centrality.
```{r eigenvector_cent, cache=TRUE}
eig <- centr_eigen(g)
V(g)$color <- "gray"
V(g)$size <- eig$vector*15
V(g)$label <- NA
plot(g)
eig$vector
V(g)[which.max(V(g)$size)]
```  

As expected, CatcherGG is the most central.

#### Community strucure via short random walks
```{r random_walk_community, cache=TRUE}
fc <- walktrap.community(g)
memb <- membership(fc)
plot(g, vertex.size=5, vertex.label=V(g)$name,vertex.color=memb+1, asp=FALSE)
#number of communities and they size
table(memb)
#the modularity
modularity(fc)
```  


#### Girvan-Newman community detection algorithm
```{r Girvan_Newman_community, cache=TRUE}
gnc <- edge.betweenness.community(g, directed=FALSE)
memb2 <- membership(gnc)
plot(g, vertex.size=5, vertex.label=V(g)$name,vertex.color=memb2+1, asp=FALSE)
#number of communities and their size
table(memb2)
#the modularity
modularity(gnc)
```  


### Insights:
1. There are 7 disjoint cliques. When taking a closer look at the people in each cliques it was possible to easily tag them: University, Army, English / Hebrew twitter persons, ...
2. It wasn't a suprise that CatcherGG would be in the middle since we know that everyone follows him.
3. There is one clique which is made of people that almost has no followers, And they are connected with themselves and a few others. Some of them are bots and some of them are new people that are not active this days.